Variance reduction for MCMC methods via martingale representations

### 2020-01-19 aap/Revision/vr-mcmc-revision.tex
update

The expression
$\sum_{p=l}^q \gamma_{p+1} \partial_{y_l}^K f(X_p)$
can be viewed as a deterministic function of
$X_{l-1},Z_l,Z_{l+1},\ldots,Z_q$
\sum_{p=l}^q \gamma_{p+1} \partial_{y_l}^K f(X_p)
=F(X_{l-1},Z_l,Z_{l+1},\ldots,Z_q).
By the (conditional) Gaussian Poincar\'e inequality,
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right]
\le\mathsf E\left[\left.
\|\nabla_Z F(X_{l-1},Z_l,Z_{l+1},\ldots,Z_q)\|^2
\right|X_{l-1}\right],
where $\nabla_Z F=(\partial_{Z_l} F,\ldots,\partial_{Z_q} F)$,
and $\|\cdot\|$ denotes the Euclidean norm.
Notice that \(\partial_{Z_j} F=\sqrt{\gamma_j}\,\partial_{y_j} F\) and
hence
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right]\leq\sum_{j=l}^{q}\gamma_{j}\mathsf{E}\left[\left(\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{j}}\partial_{y_{l}}^{K}f\left(X_{p}\right)\right)^{2}\Big|X_{l-1}\right].
It is straightforward to check that
$\partial_{y_j}\partial_{y_l}^K f(X_p)=0$
whenever $p<j$. Therefore, we get
\begin{equation}\label{eq:10062018a2}
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right]\leq\sum_{j=l}^{q}\gamma_{j}\mathsf{E}\left[\left(\sum_{p=j}^{q}\gamma_{p+1}\partial_{y_{j}}\partial_{y_{l}}^{K}f\left(X_{p}\right)\right)^{2}\Big|X_{l-1}\right].
Now fix $p$ and $j$, $p\ge j$, in $\{l,\ldots,q\}$.
By Fa\`a di Bruno's formula
\partial_{y_{l}}^{K}f\left(X_{p}\right)=\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p})\prod_{k=1}^{K}\left(\frac{\partial_{y_{l}}^{k}X_{p}}{k!}\right)^{m_{k}},
where the sum is taken over all $K$-tuples of nonnegative integers
$(m_1,\ldots,m_K)$ satisfying
1\cdot m_{1}+2\cdot m_{2}+\ldots+K\cdot m_{K}=K.
Then
\partial_{y_{j}}\partial_{y_{l}}^{K}f\left(X_{p}\right)
&=&\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K}+1)}(X_{p})\left[\partial_{y_{j}}X_{p}\right]\prod_{k=1}^{K}\left(\frac{\partial_{y_{l}}^{k}X_{p}}{k!}\right)^{m_{k}} \\
&&+\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p})
\sum_{s=1}^{K}\frac{m_{s}}{s!}
\left(\frac{\partial_{y_{l}}^{s}X_{p}}{s!}\right)^{m_{s}-1}
&& \times\left[\partial_{y_{j}}\partial_{y_{l}}^{s}X_{p}\right]
\prod_{k\le K,\,k\neq s}\left(\frac{\partial_{y_{l}}^{k}X_{p}}{k!}\right)^{m_{k}}.
Using the bounds of
Lemmas \ref{lem:06062018a2} and~\ref{lem:06062018a3},
we obtain
\label{eq:part-part}
\left|\partial_{y_{j}}\partial_{y_{l}}^{K}f\left(X_{p}\right)\right|
\leq A_{K}\prod_{k=l+1}^{p}\alpha_{k}
with a suitable constant $A_{K}$.
Substituting this in~\eqref{eq:10062018a2},
we proceed as follows
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right]
A_{K}^{2}\sum_{j=l}^{q}\gamma_{j}
\mathsf{E}\left(\sum_{p=j}^{q}\gamma_{p+1}\prod_{k=l+1}^{p}\alpha_{k}\right)^{2}
\frac{A_{K}^{2}}{(1-\gamma_1 B_\mu)^2}
\sum_{j=l}^{q} \gamma_{j}
\left(
\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=l+1}^{p} \alpha_{k}
\right)^{2}
%&=
%\frac{A_{K}^{2}}{(1-\gamma_1 b_\mu)^2}
%\sum_{j=l}^{q} \gamma_{j}
%\prod_{k=l+1}^{j} \alpha_{k}^2
%\left(
%\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
%\right)^{2}
%\\
\frac{A_{K}^{2}}{(1-\gamma_1 B_\mu)^3}
\sum_{j=l}^{q} \gamma_{j}
\prod_{k=l}^{j} \alpha_{k}
\left(
\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
\right)^{2}
\frac{A_{K}^{2}}{(1-\gamma_1 B_\mu)^3}C^3=B_K,
where $C$ is the bound from~\eqref{eq:17042018a1}.
The proof is completed.
\begin{remark}\label{rem:p-norm}
In fact in the proof of Lemma~\ref{lem:var_poincare} using \eqref{eq:part-part} we have shown that the expectations
\mathsf E\left[\left.
\|\nabla_Z F(X_{l-1},Z_l,Z_{l+1},\ldots,Z_q)\|^r
\right|X_{l-1}\right]
are uniformly bounded for all natural \(l\leq q\) and any \(r\geq 2.\) Indeed it follows from \eqref{eq:17042018a1} that  the quantities
\left(\sum_{j=l}^{q} \gamma_{j}
\prod_{k=l}^{j} \alpha_{k}\right)^{r/2}
\left(
\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
\right)^{r}
are bounded. This stronger result in combination with a \(L^r\)-Sobolev-type inequalities (see e.g. \cite{Adamczak}) implies that also higher order conditional (on \(X_{l-1}\)) central moments of the r.v.
\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)
are uniformly bounded in \(l\leq q\) and \(p.\)

@@

\section{Bounds for moments of  ULA}
For $\gamma>0$, the Markov kernel $R_\gamma$
on $(\mathbb R^d,\mathcal B(\mathbb R^d))$
is defined by
$$
R_\gamma(x,A)=\int_{A} \frac{1}{(4 \pi \gamma)^{d/2}} \text{ exp} \left\{ -\frac{1}{4\gamma} \left\| y - x + \gamma \nabla U(x)\right\|^2\right\}dy,\quad A\in \mathcal B(\mathbb R^d),
$$
while, for $k,l\in\mathbb N$, $k\le l$,
the kernel $Q_{\boldsymbol{\gamma}}^{k,l}$ is
$
Q_{\boldsymbol{\gamma}}^{k,l}=R_{\gamma_l}\cdots R_{\gamma_k}.
$
 We make the following assumptions.

\begin{description}
\item[(H1)] Assume that $\nabla U$ is Lipschitz, that is, there exists $L\geq 0$ such that 
\begin{eqnarray*}
\|\nabla U(x)-\nabla U(y)\|\leq L\|x-y\|, \quad x,y\in \mathbb{R}^d.
\end{eqnarray*}

\item[(H2)] There exist $K>0,$ $M>0$ and $m>0$ such that for any $x\not\in B_K(0)	$ and any $y\in \mathbb{R}^d$ it holds 
\begin{eqnarray*}
\langle D^2U(x)y,y\rangle \geq m\|y\|^2, \quad \|D^3 U(y)\| \leq M. 
\end{eqnarray*}

\begin{thm}
Suppose that
\begin{eqnarray*}
\sum_{p=1}^{\infty} \gamma_p=\infty, \quad \sum_{p=1}^{\infty} \gamma^2_p<\infty.
\end{eqnarray*}
Under assumptions (H1) and (H2), then for any bounded function $g$ on $\mathbb{R}^d$ 
we have
\begin{eqnarray*}
\mathsf{E}\left[\left(\sum_{p=l}^{N+n}\omega_{p,n}^{N}g(X_{p})-\bar Q_l(X_l)\right)^{4}\right] \lesssim \frac{1}{\Gamma^4_{N+2,N+n+1}}
\end{eqnarray*}
 and
\begin{eqnarray*}
\bar Q_l(X_l)=\mathsf{E}\left[\left.\sum_{p=l}^{N+n}\omega_{p,n}^{N}f(X_{p})\right|X_{l}\right].
\end{eqnarray*}
Moreover, 
\begin{eqnarray*}
\mathsf{E}\left[\exp\left(\rho\left(\sum_{k=l}^{p}\gamma_{k+1}g(X_{k})-\left(\sum_{k=l}^{p}\gamma_{k+1}\right)\pi(g)\right)\right)\right]\leq C
\end{eqnarray*}
for some small enough $\rho>0,$  all natural $0<l\leq p<\infty$ and constant $C$ not depending on $l,p.$
\end{thm}

>>>>

\begin{proof}
The expression
$\sum_{p=l}^q \gamma_{p+1} \partial_{y_l}^K f(X_p)$
can be viewed as a deterministic function of
$X_{l-1},Z_l,Z_{l+1},\ldots,Z_q$
$$
\sum_{p=l}^q \gamma_{p+1} \partial_{y_l}^K f(X_p)
=F(X_{l-1},Z_l,Z_{l+1},\ldots,Z_q).
$$
By the (conditional) Gaussian Poincar\'e inequality,
we have
$$
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right]
\le\mathsf E\left[\left.
\|\nabla_Z F(X_{l-1},Z_l,Z_{l+1},\ldots,Z_q)\|^2
\right|X_{l-1}\right],
$$
where $\nabla_Z F=(\partial_{Z_l} F,\ldots,\partial_{Z_q} F)$,
and $\|\cdot\|$ denotes the Euclidean norm.
Notice that \(\partial_{Z_j} F=\sqrt{\gamma_j}\,\partial_{y_j} F\) and
hence
$$
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right]\leq\sum_{j=l}^{q}\gamma_{j}\mathsf{E}\left[\left(\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{j}}\partial_{y_{l}}^{K}f\left(X_{p}\right)\right)^{2}\Big|X_{l-1}\right].
$$
It is straightforward to check that
$\partial_{y_j}\partial_{y_l}^K f(X_p)=0$
whenever $p<j$. Therefore, we get
\begin{equation}\label{eq:10062018a2}
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right]\leq\sum_{j=l}^{q}\gamma_{j}\mathsf{E}\left[\left(\sum_{p=j}^{q}\gamma_{p+1}\partial_{y_{j}}\partial_{y_{l}}^{K}f\left(X_{p}\right)\right)^{2}\Big|X_{l-1}\right].
\end{equation}
Now fix $p$ and $j$, $p\ge j$, in $\{l,\ldots,q\}$.
By Fa\`a di Bruno's formula
\[
\partial_{y_{l}}^{K}f\left(X_{p}\right)=\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p})\prod_{k=1}^{K}\left(\frac{\partial_{y_{l}}^{k}X_{p}}{k!}\right)^{m_{k}},
\]
where the sum is taken over all $K$-tuples of nonnegative integers
$(m_1,\ldots,m_K)$ satisfying
$$
1\cdot m_{1}+2\cdot m_{2}+\ldots+K\cdot m_{K}=K.
$$
Then
\begin{eqnarray*}
\partial_{y_{j}}\partial_{y_{l}}^{K}f\left(X_{p}\right)
&=&\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K}+1)}(X_{p})\left[\partial_{y_{j}}X_{p}\right]\prod_{k=1}^{K}\left(\frac{\partial_{y_{l}}^{k}X_{p}}{k!}\right)^{m_{k}} \\
&&+\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p})
\sum_{s=1}^{K}\frac{m_{s}}{s!}
\left(\frac{\partial_{y_{l}}^{s}X_{p}}{s!}\right)^{m_{s}-1}
\\
&& \times\left[\partial_{y_{j}}\partial_{y_{l}}^{s}X_{p}\right]
\prod_{k\le K,\,k\neq s}\left(\frac{\partial_{y_{l}}^{k}X_{p}}{k!}\right)^{m_{k}}.
\end{eqnarray*}
Using the bounds of
Lemmas \ref{lem:06062018a2} and~\ref{lem:06062018a3},
we obtain
\begin{eqnarray}
\label{eq:part-part}
\left|\partial_{y_{j}}\partial_{y_{l}}^{K}f\left(X_{p}\right)\right|
\leq A_{K}\prod_{k=l+1}^{p}\alpha_{k}
\end{eqnarray}
with a suitable constant $A_{K}$.
Substituting this in~\eqref{eq:10062018a2},
we proceed as follows
\begin{align*}
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right]
&\le
A_{K}^{2}\sum_{j=l}^{q}\gamma_{j}
\mathsf{E}\left(\sum_{p=j}^{q}\gamma_{p+1}\prod_{k=l+1}^{p}\alpha_{k}\right)^{2}
\\
&\le
\frac{A_{K}^{2}}{(1-\gamma_1 B_\mu)^2}
\mathsf{E}\sum_{j=l}^{q} \gamma_{j}
\left(
\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=l+1}^{p} \alpha_{k}
\right)^{2}
\\
%&=
%\frac{A_{K}^{2}}{(1-\gamma_1 b_\mu)^2}
%\sum_{j=l}^{q} \gamma_{j}
%\prod_{k=l+1}^{j} \alpha_{k}^2
%\left(
%\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
%\right)^{2}
%\\
&\le
\frac{A_{K}^{2}}{(1-\gamma_1 B_\mu)^3}
\mathsf{E}\sum_{j=l}^{q} \gamma_{j}
\prod_{k=l}^{j} \alpha_{k}
\left(
\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
\right)^{2}
\end{align*}

%\som{Changed exponent from 1/2 to 2 here}
Now, from Hoelder inequality, we obtain (with $\|X\|_p = (\mathsf{E}X^p)^{\frac{1}{p}}$)
\begin{align*}
\mathsf{E}\left[\sum_{j=l}^{q}\gamma_{j}\prod_{k=l}^{j}\alpha_{k}\left(\sum_{p=j+1}^{q+1}\gamma_{p}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right] & \leq\sum_{j=l}^{q}\gamma_{j}\left\Vert \prod_{k=l}^{j}\alpha_{k}\right\Vert _{2}\left\Vert \sum_{p=j+1}^{q+1}\gamma_{p}\prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}^{2}\\
 & \leq\sum_{j=l}^{q}\gamma_{j}\left\Vert \prod_{k=l}^{j}\alpha_{k}\right\Vert _{2}\left(\sum_{p=j+1}^{q+1}\gamma_{p}\left\Vert \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}\right)^{2}.
\end{align*}
Now using the fact that $\prod\limits_{k=j+1}^{p}\alpha_{k} \leq \exp\left(-\sum\limits_{k=j+1}^{p}\gamma_{k}\mu'(X_{k-1})\right),$
we get 
\[
\mathsf{E}\left[\sum_{j=l}^{q}\gamma_{j}\prod_{k=l}^{j}\alpha_{k}\left(\sum_{p=j+1}^{q+1}\gamma_{p}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right]\leq\sum_{j=l}^{q}\gamma_{j} \zeta^{1/2}_{l,j}(2) \left(\sum_{p=j+1}^{q+1}\gamma_{p} \zeta^{1/4}_{j+1,p}(4)\right)^{2},
\]
where we denote
\[
\zeta_{l,j}(s)=\mathsf{E}\left[e^{-s\sum_{k=l}^{j}\gamma_{k}\mu'(X_{k-1})}\right],\quad s>0.
\]
From Theorem~\ref{exp_mom_ula} in Appendix~\ref{sec:appendix}, it follows that
\[
\zeta_{l,j}(s) \leq e^{s\kappa \Gamma^*}e^{-2s\Gamma_{l,j}\alpha}
\]
with $\Gamma^* = \sum\limits_{k=1}^{\infty}\gamma_k^2, \kappa = ..., \Gamma_{l,j} = \sum\limits_{k=l}^{j}\gamma_k, \alpha = \int \mu^2(x)\pi(x)\,dx$. Since $\sum\limits_{k=1}^{\infty}\gamma_k = \infty$, we may bound
\begin{align*}
\sum\limits_{p=j+1}^{\infty} \gamma_p e^{-2\alpha \Gamma_{j+1,p}} < \int\limits_{0}^{+\infty}e^{-2\alpha x}\,dx = \frac{1}{2\alpha}
\end{align*}
yielding 
\begin{align*}
\sum_{p=j+1}^{q+1}\gamma_{p} \zeta^{1/4}_{j+1,p}(4) \leq e^{\kappa \Gamma^*}\sum_{p=j+1}^{q+1}\gamma_{p}e^{-2\alpha \Gamma_{j+1,p}} \leq \frac{e^{\kappa \Gamma^*}}{2\alpha} 
\end{align*}
Using the same integral bound, 
\begin{align*}
\mathsf{E}\left[\sum_{j=l}^{q}\gamma_{j}\prod_{k=l}^{j}\alpha_{k}\left(\sum_{p=j+1}^{q+1}\gamma_{p}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right] \leq
\frac{e^{2\kappa \Gamma^*}}{2\alpha}\sum_{j=l}^{q}\gamma_{j}e^{-2\alpha \Gamma_{l,j}} \leq \frac{e^{2\kappa \Gamma^*}}{4\alpha^2}
\end{align*}
Plugging into bound for conditional variance, 
\begin{align*}
\mathsf{Var}\left[\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)\Big|X_{l-1}\right] \leq
\frac{A_{K}^{2}e^{2\kappa \Gamma^*}}{4\alpha^2(1-\gamma_1 B_\mu)^3}
\end{align*}
\par
The proof is completed.
\end{proof}
\begin{remark}\label{rem:p-norm}
In fact in the proof of Lemma~\ref{lem:var_poincare} using \eqref{eq:part-part} we have shown that the expectations
\begin{eqnarray*}
\mathsf E\left[\left.
\|\nabla_Z F(X_{l-1},Z_l,Z_{l+1},\ldots,Z_q)\|^r
\right|X_{l-1}\right]
\end{eqnarray*}
are uniformly bounded for all natural \(l\leq q\) and any \(r\geq 2.\) Indeed it follows from \eqref{eq:17042018a1} that  the quantities
\begin{eqnarray*}
\left(\sum_{j=l}^{q} \gamma_{j}
\prod_{k=l}^{j} \alpha_{k}\right)^{r/2}
\left(
\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
\right)^{r}
\end{eqnarray*}
are bounded. This stronger result in combination with a \(L^r\)-Sobolev-type inequalities (see e.g. \cite{Adamczak}) implies that also higher order conditional (on \(X_{l-1}\)) central moments of the r.v.
\begin{eqnarray*}
\sum_{p=l}^{q}\gamma_{p+1}\partial_{y_{l}}^{K}f\left(X_{p}\right)
\end{eqnarray*}
are uniformly bounded in \(l\leq q\) and \(p.\)

@@

\section{Bounds for moments of  ULA}\label{sec:appendix}
For $\gamma>0$, the Markov kernel $R_\gamma$
on $(\mathbb R^d,\mathcal B(\mathbb R^d))$
is defined by
$$
R_\gamma(x,A)=\int_{A} \frac{1}{(4 \pi \gamma)^{d/2}} \text{ exp} \left\{ -\frac{1}{4\gamma} \left\| y - x + \gamma \nabla U(x)\right\|^2\right\}dy,\quad A\in \mathcal B(\mathbb R^d),
$$
while, for $k,l\in\mathbb N$, $k\le l$,
the kernel $Q_{\boldsymbol{\gamma}}^{k,l}$ is
$
Q_{\boldsymbol{\gamma}}^{k,l}=R_{\gamma_l}\cdots R_{\gamma_k}.
$
 We make the following assumptions.

\begin{description}
\item[{\bf (H1)}] Assume that $\nabla U$ is Lipschitz, that is, there exists $L\geq 0$ such that 
\begin{eqnarray*}
\|\nabla U(x)-\nabla U(y)\|\leq L\|x-y\|, \quad x,y\in \mathbb{R}^d.
\end{eqnarray*}

\item[{\bf (H2)}] There exist $K>0,$ $M>0$ and $m>0$ such that for any $x\not\in B_K(0)	$ and any $y\in \mathbb{R}^d$ it holds 
\begin{eqnarray*}
\langle D^2U(x)y,y\rangle \geq m\|y\|^2, \quad \|D^3 U(y)\| \leq M. 
\end{eqnarray*}
\end{description}

Due to \cite[Lemma~14]{brosse:2018:diffusion}, it is known that conditions (H1) and (H2) imply the result

\begin{description}
\item[{\bf (H3)}] There exist $K_1 > 0, m > 0$, such that for any $x \not\in B_{K_1}(0)$ it holds
\begin{eqnarray*}
\langle \nabla U(x), x \rangle \geq \frac{m}{2}\|x\|^2
\end{eqnarray*}
\end{description}

\begin{lem} Assume that the potential $U(x), x \in \mathbb{R}^D$ satisfies conditions {\bf (H1)} and {\bf (H3)} and without loss of generality consider $\nabla U(0) = 0$. Then the kernel \ref{} satisfies drift condition \ref{eq:drift} for any $0 < \gamma < \overline{\gamma} = \frac{m}{4L^2}$ with drift function $V(x) = 1 + \|x\|^2$, constants $\lambda = \exp{-\left(\frac{m}{2}\right)}$, $C = 3K_1^2 + 2D + C_1$ for some absolute constant $C_1 > 0$, , which does not depend on $\gamma, D, x$.
\end{lem}

\begin{proof} Consider $V(x) = 1 + \|x\|^2$, then
$$
P_{\gamma}V(x) = \int\limits_{\mathbb{R}^d}V(y)P_{\gamma}(x,dy) = \int\limits_{\mathbb{R}^d}(1+\|y\|^2)\frac{1}{(4\pi\gamma)^{\frac{d}{2}}}\exp{\left(-\frac{\|y-x+\gamma\nabla U(x)\|^2}{4\gamma}\right)}\,dy = 
$$

$$
=1 + \frac{1}{(4\pi\gamma)^{\frac{d}{2}}}\int\limits_{\mathbb{R}^d}\|z + x - \gamma \nabla U(x)\|^2 \exp{\left(-\frac{\|z\|^2}{4\gamma}\right)}\,dz
$$
Let us first consider the case $x \notin B(0,K_1)$. Note that $\|z+x-\gamma \nabla U(x)\|^2 = \|z\|^2 + 2 \langle z, x - \gamma \nabla U(x) \rangle + \gamma^2 \|x - \gamma \nabla U(x)\|^2$ and the linear term vanishes after integration, moreover, for $Z \sim \mathcal{N}(0,2\gamma I_d$, it holds $\mathbb{E}\|Z\|^2 = 2\gamma d$. It remains to notice that due to {\bf C1} and {\bf C2}
$$
\|x - \gamma \nabla U(x) \|^2 = \|x\|^2 - 2\gamma \langle \nabla U(x), x\rangle + \gamma^2 \|\nabla U(x)\|^2 \leq
$$
$$
 \leq (1-\gamma m)\|x\|^2 + 2\gamma^2 L^2 \|x\|^2
$$
Thus, plugging everything into expression for $P_{\gamma}V$ and using $\gamma < \frac{m}{4L}$, we obtain
$$
P_{\gamma}V(x) \leq (1-\gamma m + 2\gamma^2 L^2)V(x) + 2\gamma d + (\gamma m - 2\gamma^2 L^2) \leq \exp^{-\frac{\gamma m}{2}}V(x) + 2\gamma d
$$
Now let $x \in B(0,K_1)$. Then simply using $\|x-\gamma \nabla U(x)\|^2 \leq 2(1+L\gamma)^2\|x\|^2$, we obtain
$$
P_{\gamma}V(x) \leq (1-\gamma m + 2\gamma^2 L^2)V(x) + \gamma\left((m - 2\gamma L^2)(1+\|x\|^2) + 2d + 2(1+L\gamma)^2\|x\|^d\right) \leq 
$$

$$
\leq \exp^{-\frac{\gamma m}{2}}V(x) + \gamma(3K_1^2 + 2D + C_1)
$$
for some absolute constant $C_1$.
\end{proof}

Now the geometric ergodicity result readily follows from \cite[Theorem~19.4.1]{douc:moulines:priouret:soulier:2018}, namely, the following lemma holds:

\begin{lem} Let the potential $U(x), x \in \mathbb{R}^D$ satisfy conditions {\bf H1} and {\bf H3}. Then for $0 < \gamma < \overline{\gamma}=\frac{m}{4L^2}$, for any $x \in X$ it holds
$$
d_V(\delta_xQ^n_\gamma,\pi_\gamma) \leq C\rho^n\left(V(x) + \pi_\gamma(V)\right)
$$ 
with $V(x) = 1 + \|x\|^2$ and constants
$$
b = \gamma(3K_1^2 + 2D + C_1); \quad \overline{b} = b\exp^{-\frac{m\gamma}{2}} + d; \quad \varepsilon = 2\Phi\left(-\frac{\sqrt{d}(1+L\gamma)}{2\sqrt{\gamma}}\right); \quad
$$

$$
C = \left(1 + \exp^{-\frac{m\gamma}{2}}\right)\left(1+\frac{\overline{b}}{(1-\varepsilon)(1-\exp^{-\frac{m\gamma}{2}} - \frac{2b}{1+d})}\right);
$$

$$
\rho = \exp^{-\gamma\left(\frac{m}{2} - 2\frac{3K_1^2 + 2D + C_1}{d}\right)\frac{\log{(1-\varepsilon)}}{\log{(1-\varepsilon)} + \log{(\exp^{-\frac{m\gamma}{2}} + \frac{2b}{d+1})}}}
$$
for some $C_1 > 0$, which does not depend on $d, \gamma$ and $n$.
\end{lem}

\begin{proof} Note that the condition {\bf H1} implies that the Markov kernel $Q^n_\gamma$ satisfies $(1,\varepsilon)$-Doeblin condition with $\varepsilon = 2\Phi\left(-\frac{\sqrt{d}(1+L\gamma)}{2\sqrt{\gamma}}\right)$. Together with drift condition {\bf H2} it allows to apply \cite[Theorem~19.4.1]{douc:moulines:priouret:soulier:2018} with appropriate constants. 
\end{proof}

\begin{thm}
\label{exp_mom_ula}
Suppose that
\begin{eqnarray*}
\sum_{p=1}^{\infty} \gamma_p=\infty, \quad \sum_{p=1}^{\infty} \gamma^2_p<\infty.
\end{eqnarray*}
Under assumptions {\bf (H1)} and {\bf (H2)}, for any bounded function $g$ on $\mathbb{R}^d$ 
we have
\begin{eqnarray*}
\mathsf{E}\left[\left(\sum_{p=l}^{N+n}\omega_{p,n}^{N}g(X_{p})-\bar Q_l(X_l)\right)^{4}\right] \lesssim \frac{1}{\Gamma^4_{N+2,N+n+1}}
\end{eqnarray*}
 and
\begin{eqnarray*}
\bar Q_l(X_l)=\mathsf{E}\left[\left.\sum_{p=l}^{N+n}\omega_{p,n}^{N}f(X_{p})\right|X_{l}\right].
\end{eqnarray*}
Moreover, 
\begin{eqnarray*}
\mathsf{E}\left[\exp\left(\rho\left(\sum_{k=l}^{p}\gamma_{k+1}g(X_{k})-\left(\sum_{k=l}^{p}\gamma_{k+1}\right)\pi(g)\right)\right)\right]\leq C
\end{eqnarray*}
for some small enough $\rho>0,$  all natural $0<l\leq p<\infty$ and constant $C$ not depending on $l,p.$
\end{thm}
\begin{proof}
 Note that 
\[
\mathsf{E}\left[e^{-s\sum_{k=l}^{j}\gamma_{k}\mu'(X_{k-1})}\right]=\mathsf{E}\left[e^{-s\left(\sum_{k=l}^{j}\gamma_{k}\mu'(X_{k-1})-\Gamma_{l,j}\int\mu'(x)\pi(x)\,dx\right)}\right]e^{-s\Gamma_{l,j}\int\mu'(x)\pi(x)\,dx}
\]
 with $\Gamma_{l,j}=\sum_{k=l}^{j}\gamma_{k}.$ According to \cite[Theorem~3]{bms:exp_conc_note}, it holds
\[
\mathsf{E}\left[e^{-s\left(\sum_{k=l}^{j}\gamma_{k}\mu'(X_{k-1})-\Gamma_{l,j}\int\mu'(x)\pi(x)\,dx\right)}\right]\leq e^{s\varkappa\sum_{k=l}^{j}\gamma_{k}^{2}}
\]
 for some $\varkappa>0.$ Since $\sum_{k=1}^{\infty}\gamma_{k}^{2}\leq\Gamma^{\star},$we
have 
\[
\mathsf{E}\left[e^{-s\sum_{k=l}^{j}\gamma_{k}\mu'(X_{k-1})}\right]\leq e^{s\varkappa\Gamma^{\star}}e^{-s\Gamma_{l,j}\int\mu'(x)\pi(x)\,dx}.
\]
Furthermore, since $\mu\pi',\mu'\pi\in L^{1}(\mathbb{R}),$ we have
\[
\int\mu'(x)\pi(x)\,dx=-\int\mu(x)\pi'(x)\,dx=2\int\mu^{2}(x)\pi(x)\,dx>0
\]
and as a result 
\[
\zeta_{l,j}(s)\leq e^{s\varkappa\Gamma^{\star}}e^{-2s\Gamma_{l,j}\int\mu^{2}(x)\pi(x)\,dx}
\]
 for any $l\leq j.$
\end{proof}

Suppose that now we use ULA with fixed step size, then we might use the following version of the previous theorem:
\begin{thm} Suppose that we use ULA with constant step size $\gamma$. Under assumptions {\bf (H1)} and {\bf (H2)}, for any bounded function $g$ on $\mathbb{R}^d$ we have, given $0 < \gamma < \left(\frac{\int \mu^{\prime}(x)\pi(x)\,dx}{C_1 M}\right)^2$,
\begin{eqnarray*}
\mathsf{E}\left[\exp\left(\rho\left(\sum_{k=l}^{p}\gamma_{k+1}g(X_{k})-\left(\sum_{k=l}^{p}\gamma_{k+1}\right)\pi(g)\right)\right)\right]\leq C
\end{eqnarray*}
for some absolute constant $C$ not depending on $l,p$.
\end{thm}

\begin{proof} Note that 
\begin{eqnarray*} 
\int \mu^{\prime}(x)\pi_{\gamma}(x)\,dx \geq \int \mu^{\prime}(x)\pi(x)\,dx - M d_{TV}(\pi,\pi_{\gamma}) \geq \int \mu^{\prime}(x)\pi(x)\,dx - C_1\sqrt{\gamma}M
\end{eqnarray*}
where the precise expression for constant $C_1$ might be found in \cite[Theorem~10]{durmus:moulines:aop:2016}. Thus, for $\gamma < \left(\frac{\int \mu^{\prime}(x)\pi(x)\,dx}{C_1 M}\right)^2$, we obtain along the lines of the proof of Theorem~16 that
$$
\int \mu^{\prime}(x)\pi_{\gamma}(x)\,dx > 0
$$
